\section{Problem 6}

The small-signal model of a forward-biased diode, from chapter 1 in Analog Integrated Circuit Design by Carusone, Johns and Martin (”CJM”), includes two capacitances.

\subsection*{a) Give a brief explanation about each of the two capacitive contributions and how
they emerge.}

The two capacitive contributions mentioned in the 1st chapter in Analog Integrated Circuit Design by Carusone is depletion capitance, $C_j$ and  diffusion capacitance also called diffusion capacitance $C_d$

The depletion capitance, $C_j$ arises from the depletion region of a pn-junction. This region comes from charge carriers from both side recombine, creating a region around the junction with immobile charges. This creates an electric field. When we apply reverse bias to the pn-junction, the depletion region widens, and the electric field increases. This behavior can be modeled as a parallel-plate capacitor, where the "plates" are the n-type and p-type regions separated by the depletion region.  This capacitance is given by:

\begin{equation*}
    \mathrm{C}_{\mathrm{j}}=\frac{\mathrm{C}_{\mathrm{j} 0}}{\left(1+\frac{\mathrm{V}_{\mathrm{B}}}{\Phi_{0}}\right)^{\mathrm{m}_{\mathrm{j}}}}
\end{equation*}

where

\begin{equation*}
    \mathrm{C}_{\mathrm{j} 0}=\left(1-\mathrm{m}_{\mathrm{j}}\right)\left[2 \mathrm{qK}_{\mathrm{s}} \varepsilon_{0} \frac{\mathrm{N}_{\mathrm{A}} \mathrm{N}_{\mathrm{D}}}{\mathrm{N}_{\mathrm{A}}+\mathrm{N}_{\mathrm{D}}}\right]^{1-\mathrm{m}_{\mathrm{j}}} \frac{1}{\Phi_{0}^{\mathrm{m}_{\mathrm{j}}}} 
\end{equation*}


The diffusion capitance arises from the movement of charge carriers across the junction under forward bias conditions. This process can be modelled as a capacitor storing charge. When a forward bias is applied,  $C_d$ is given by:

\begin{equation*}
    \mathrm{C}_{\mathrm{d}}=\tau_{\mathrm{T}} \frac{\mathrm{I}_{\mathrm{D}}}{\mathrm{V}_{\mathrm{T}}} 
\end{equation*}




\subsection*{b) A diode is biased for a current of $1 mA$, and has a transit time of $50 ps$. Estimate
it’s small-signal resistance and diffusion capacitance.}

By using the equation for $C_d$ above and assuming that we are in room temperature; $V_T\approx26 mV$ at roomtemperature, we get that $C_D=3.846\times 10^{-13}F$.